\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-15 trunk/arch.tex
- Reworked paragraph in the last section in resp. to Kanna's comments - corrected one bibtex entry that refused to be embedded parsed

This choice is directed not only by heuristic choices made in the
solver but also enforced by the heuristic order of the decision point
resolution choices for the {\em internal} state flaw presented in
Section \ref{sec:arch:sync} \fcomment{TODO: need to rework the
  presentation of thee choices so I can refer to them more directly --
  algorithm or pseudo theorem should do the trick}. Should such a flaw
be revealed during synchronization -- such that the current state of
an {\em internal} state variable is not fully grounded -- the
sequencing of the choices will attempt first a conservative choice in
maintaining previous state and only then try a more optimistic
approach in terms of the \comment{I don't follow this last bit. Is
  this token addition that you're talking about?} execution/advance in
our current plan to finally attempt other choices that were not
predicted by the model. The two first possible choices are strongly
directed by the existing plan which helps direct the search within
this frame. This often allow to have a synchronization that is much
more directed and, in nominal cases such as the one we showed resolve
the deliberation in few steps (often without any backtrack in the
search) \comment{All this is confusing; probably reword}.

@@

In \rx however the interaction between planning and execution does not
stop at this level. The overall scheduling of both {\em
  synchronization} and {\em planning} is such that the synchronization
can occur in between any planning step. Not only is synchronization
influenced by the outcome, but it also influences
planning. Specifically when synchronization occurs before a complete
plan is found, it will inject new facts ({\em external} observations
and resulting {\em internal} state) in the plan database available for
inference when the next planning \texttt{step} resumes. Therefore they
\comment{what is the ``they''?} are not integral part of the plan
resolution (generating potentially new flaws for the planner or
contributing to resolve previously existing flaws). The planning
process is therefore perturbed internally and fully informed by how
the world is evolving even as it is planning.  This specific aspect
contrasts with other approaches we have which avoid perturbing the
planner during its search as it is not compatible with the ``off-line
planning'' assumption.

>>>>

This choice is directed not only by heuristic choices made in the
solver but also enforced by the heuristic order of the decision point
resolution choices for the {\em current  state flaw} presented in
Proposition \ref{prop:csf:resolve}. Indeed, as we stated then the two
first choices tend to privilege a conservative view in respect to the
existing plan. It attempts first to extend the previous observation we
produced for this {\em internal} timeline in order to avoid to commit
to early in the plan advance. If the formaer failed it will then
attempt to start the next exisiting token in the plan which alow the
reactor to advance its plan execution. Both of these two initial
choices atetempt to resolve the plan with the least amount of
perturbation of the plan. They just constrain further the start and
end time of the exisiting tokens which were provided by the previous 
deliberations steps. This means that in a nominal situation where the
plan this reactor produced is properly executed, the synchronization
remains limited to restrict time points in the plan and progate their
impact. Most of the heavy dutty work of creating new tokens in the
plan and schedule them -- both being much more difficult problems 
to resolve -- have been managed during deliberation steps. In that
sense we see that most of the time synchronization is limited to very
few node in \eu search space with often no backtrack required. The
synchronization may become slightly nore costfull when we need to
identify a new token to be injected by the plan (the 3rd choice in
Proposition \ref{prop:csf:resolve}) as it needs to explore on tis own
all the possible token types this timeline accept as value. This is
the reason this choice is evaluated last in our flaw resolution in
order to avoid such complex action during synchronization unless 
necessary. In that sense,  ansd due to carefull choice on our
synchrponization heurisitic we see that the plan produced during \rx
deliberation steps helps sthe synchronization process to be more
efficient.

% Should such a flaw be revealed 
% during synchronization -- such that the current state of
% an {\em internal} state variable is not fully grounded -- the
% sequencing of the choices will attempt first a conservative choice in
% maintaining previous state and only then try a more optimistic
% approach in terms of the \comment{I don't follow this last bit. Is
%   this token addition that you're talking about?} execution/advance in
% our current plan to finally attempt other choices that were not
% predicted by the model. The two first possible choices are strongly
% directed by the existing plan which helps direct the search within
% this frame. This often allow to have a synchronization that is much
% more directed and, in nominal cases such as the one we showed resolve
% the deliberation in few steps (often without any backtrack in the
% search) \comment{All this is confusing; probably reword}.

@@

In \rx however the interaction between planning and execution does not
stop at this level. The overall scheduling of both {\em
  synchronization} and {\em planning} is such that the synchronization
can occur in between any planning step. Not only is synchronization
influenced by the outcome, but it also influences
planning. Specifically when synchronization occurs before a complete
plan is found, it will inject new facts ({\em external} observations
and resulting {\em internal} state) in the plan database available for
inference when the next planning \texttt{step} resumes. On this next
step the \eu solver used for planning will have these new facts
included in the partial plan which can introduce new flaws in the plan
while potetnially having reolved previously exisiting flaw. The
deliberation process is therefore perturbed externally by the {\em
  synchronization} and consequently fully informed of the world state
evolution as it is planning.  This specific aspect contrasts with
other more classical approaches we have seen, which avoid 
perturbing the planner during its search as it is not compatible 
with the ``off-line planning'' assumption.
